---
title: "Bayescoverage APP - overview"
author: "Leontine Alkema, last updated June 8, 2026"
format: pdf
editor: visual
---

Installation info is given in the readme and shinyapp

```{r}
#| label: setup
library(bayescoveragedeploy)
```

Where data are stored:

```{r}
data_folder <- "data_raw" # for survey data 
routinedata_dir <- here::here("private/routinedata/")
# see note on working with routine dummy data below
```

Choose an indicator. Naming comes from survey data, options include

-   c("anc1trimester", "vmsl", "ideliv", "vdpt", "anc4") , with routine as available

-   c("bfexcl0_5", "ancq8" , "cci" , "sba" ), no routine data

```{r}
indicator_select <- "anc1trimester"#"anc4" #"cci"#"vdpt"#"anc4""anc4"#
```

Read in survey data and process

```{r}
dat0 <- haven::read_dta(here::here(data_folder, "ICEH_all.long_20260603.dta")) |>
  dplyr::rename(r = r_raw, se = se_raw) 
```

Fitting for one country, use ISO to select

```{r}
# countries with survey data
# unique(dat$iso)
iso_select <- "KEN" #RWA"
dat_use <- 
  bayescoveragemodel::process_data(
  dat = dat0 |> 
  dplyr::filter(iso %in% iso_select),
  regions_dat = bayescoveragemodel::regions_all,
  indicator = indicator_select, verbose = FALSE)
```

Do we want to add routine data?

```{r}
add_routine <- ifelse(
  indicator_select %in% c("anc1trimester", "vmsl", "ideliv", "vdpt", "anc4"),
  TRUE, 
  FALSE)
add_routine
```

If yes, read in routine data.

```{r}
if (!add_routine){
  routine_dat  <- routine_dat_use <- NULL
} else {
  # # if we want to use real data
  # routine_dat_raw <- readr::read_csv(
  #   here::here("private/routinedata/routine_data_all.csv"),
  #                                       show_col_types = FALSE)
  #   routine_dat_use <- routine_dat_raw |>
  #             dplyr::filter(iso == iso_select, indicator_name == indicator_select)
            
  # or if we want to use dummy data
  routine_dat_use <- readr::read_csv(here::here("data_raw/routine_toydata.csv")) |>
  # add iso
  dplyr::mutate(iso = iso_select,
                     indicator_name = indicator_select)
}
routine_dat_use

# or use a dummy set as follows:
# routine_dat_use <- data.frame(
#   iso = rep(iso_select, 3),
#    year = 2021:2023,
#   indicator_name = indicator_select,
#   routine_value = c(0.85, 0.87, 0.90),
#   countdownmean = rep(100, 3))
```


```{r}
fit <- bayescoveragedeploy::fit_local_model(
          survey_df = dat_use,
          indicator = indicator_select, 
          iso_select  = iso_select,
          routine_df = routine_dat_use,
          # these sampling settings are the new defaults in updated deploy package
          # so not needed if you use deploy 0.2 or higher
          iter_sampling = 300,
          iter_warmup = 150,
          adapt_delta = 0.95,
          max_treedepth = 14
        )
```

Overview plot

```{r}
countryplot <- bayescoveragemodel::plot_estimates_local_all(
  results = fit,
  save_plots = FALSE)[[1]]
countryplot
```

Estimates

```{r}
fit$posteriors$temporal |>
  dplyr::select(iso, year, `50%`, `2.5%`, `97.5%`) 
```

Compare to a fit w/o routine data (if routine data were added)

```{r}
fit_noroutine<- bayescoveragedeploy::fit_local_model(
          survey_df = dat_use,
          indicator = indicator_select, 
          iso_select  = iso_select,
          routine_df = NULL, 
          # these sampling settings are the new defaults in updated deploy package
          # so not needed if you use deploy 0.2 or higher
          iter_sampling = 300,
          iter_warmup = 150,
          adapt_delta = 0.95,
          max_treedepth = 14
        )
countryplot <- bayescoveragemodel::plot_estimates_local_all(
  results = fit,
  results2 = fit_noroutine,
  modelnames = c("with routine", "without routine"),
  save_plots = FALSE)[[1]]
countryplot
```

