---
title: "Bayescoverage APP - subnational overview"
author: "Leontine Alkema, last updated June 12, 2026"
format: pdf
editor: visual
---

Installation info is given in the readme and shinyapp

```{r}
#| label: setup
library(bayescoveragedeploy)
```

Where data are stored:

```{r}
data_folder <- "data_raw" # for survey data 
routinedata_dir <- here::here("private/routinedata/")
# see note on working with routine dummy data below
```

Choose an indicator. Naming comes from survey data, options include

-   c("anc1trimester", "vmsl", "ideliv", "vdpt", "anc4") , with routine as available

-   c("bfexcl0_5", "ancq8" , "cci" , "sba" ), no routine data


NOTE JUNE 12: ONLY CCI and ANC4 can be used right now

```{r}
indicator_select <- "anc4" #"cci"
```

Read in survey data and process

```{r}
dat0 <- haven::read_dta(here::here(data_folder, "ICEH_gregion_20260611.dta")) |>
  dplyr::rename(r = r_raw, se = se_raw, , admin1 = "level")
```

If relevant, LA added code to clean the 6/11 data set to only keep only years with same regional structure as most recent year (as some countries have different regions for different surveys).

Copying here in quarto but not used.


```{r, eval = FALSE}

# Filter to 
# For each iso-indic combination:
# 1. Find the most recent year
# 2. Get the unique regions in that year
# 3. Keep only years where regions match the most recent year
dat1 <- dat0 |>
  dplyr::group_by(iso, indic) |>
  dplyr::mutate(
    max_year = max(year, na.rm = TRUE)
  ) |>
  dplyr::group_by(iso, indic, year) |>
  dplyr::mutate(
    regions_this_year = paste(sort(unique(admin1)), collapse = "|")
  ) |>
  dplyr::group_by(iso, indic) |>
  dplyr::mutate(
    regions_max_year = regions_this_year[year == max_year][1]
  ) |>
  dplyr::filter(regions_this_year == regions_max_year) |>
  dplyr::select(-max_year, -regions_this_year, -regions_max_year) |>
  dplyr::ungroup()
```


Fitting for 1 or more regions in one country, use ISO to select

```{r}
# countries with survey data
# unique(dat$iso)
iso_select <- "NGA"
dat_use <- 
  bayescoveragemodel::process_data(
  dat = dat0 |> 
  dplyr::filter(iso %in% iso_select),
  regions_dat = bayescoveragemodel::regions_all,
  indicator = indicator_select, verbose = FALSE)
# regions
admin1s <- sort(unique(dat_use$admin1))
admin1s
```

Do we want to add routine data?

```{r}
add_routine <- ifelse(
  indicator_select %in% c("anc1trimester", "vmsl", "ideliv", "vdpt", "anc4"),
  TRUE, 
  FALSE)
add_routine
```

If yes, read in routine data. Make sure it has an admin1 column with admin1 names that match the survey data. DO NOT include an iso column in the routine data set. 

```{r}
if (!add_routine){
  routine_dat  <- routine_dat_use <- NULL
} else {
  # use dummy data, need
  routine_dat_use <-  readr::read_csv(here::here("data_raw/routine_toydata.csv")) |>
  # add admin1 column with matching names to dat_use
  dplyr::mutate(admin1 = admin1s[1], 
                     indicator_name = indicator_select) |>
  dplyr::select(-iso) 
}
routine_dat_use

# or use a dummy set as follows:
# routine_dat_use <- data.frame(
#   iso = rep(iso_select, 3),
#    year = 2021:2023,
#   indicator_name = indicator_select,
#   routine_value = c(0.85, 0.87, 0.90),
#   countdownmean = rep(100, 3))
```

make sure to use the "subnational = TRUE" argument to fit the model.
Just fitting here to the region where we have routine data

```{r}
fit <- bayescoveragedeploy::fit_local_model(
          survey_df = dat_use |> dplyr::filter(admin1 %in% routine_dat_use$admin1),
          subnational = TRUE, 
          indicator = indicator_select, 
          iso_select  = iso_select,
          routine_df = routine_dat_use
        )
```

Overview plot

```{r}
countryplot <- bayescoveragemodel::plot_estimates_local_all(
  results = fit,
  save_plots = FALSE)
countryplot[[1]]
```

Estimates

```{r}
fit$posteriors$temporal |>
  dplyr::select(iso, admin1, year, `50%`, `2.5%`, `97.5%`) 
```

Compare to a fit w/o routine data, all regions here

```{r}
fit_noroutine<- bayescoveragedeploy::fit_local_model(
  # fit just for the first region
          survey_df = dat_use,
          subnational = TRUE, 
          indicator = indicator_select, 
          iso_select  = iso_select,
          routine_df = NULL)
countryplot <- bayescoveragemodel::plot_estimates_local_all(
  results = fit,
  results2 = fit_noroutine,
  region_codes = routine_dat_use$admin1[1],
  modelnames = c("with routine", "without routine"),
  save_plots = FALSE)
countryplot[[1]]
```

Add comparison plot
```{r}
p <- bayescoveragemodel::plot_subnational_comparison(results  = fit,
                                 results2 = fit_noroutine,
                                 model_names = c("Model w routine data",
                                                "Model w/o routine data"),
                                 year_select  = 2025)
p
```

