---
title: "Bayescoverage APP - overview"
author: "Leontine Alkema, last updated June 1, 2026"
format: pdf
editor: visual
---

Installation info is given in the readme and shinyapp

```{r}
#| label: setup
library(bayescoveragedeploy)
```

Where data are stored:

```{r}
data_folder <- "data_raw" # for survey data 
routinedata_dir <- here::here("private/routinedata/")
# see note on working with routine dummy data below
```

Choose an indicator. Naming comes from survey data, options include

-   c("anc1trimester", "vmsl", "ideliv", "vdpt", "anc4") , with routine as available

-   c("bfexcl0_5", "ancq8" , "cci" , "sba" ), no routine data

```{r}
indicator_select <-"anc4" #"cci"#"vdpt"#"anc4"
```

Read in survey data and process

```{r}
dat0 <- haven::read_dta(here::here(data_folder, "ICEH_all.long.dta")) |>
  dplyr::rename(r = r_raw, se = se_raw) 
# process for indicator_select
dat <- bayescoveragemodel::process_data(
  dat = dat0,
  regions_dat = bayescoveragemodel::regions_all,
  indicator = indicator_select)
```

Fitting for one country, use ISO to select

```{r}
# countries with survey data
# unique(dat$iso)
iso_select <- "RWA"
dat_use <- 
  dat |> 
  dplyr::filter(iso %in% iso_select)
```

Do we want to add routine data?

```{r}
add_routine <- ifelse(
  indicator_select %in% c("anc1trimester", "vmsl", "ideliv", "vdpt", "anc4"),
  TRUE, 
  FALSE)
add_routine
```

If yes, read in routine data.

```{r}
if (!add_routine){
  routine_dat  <- routine_dat_use <- NULL
} else {
  # if we want to use real data
  # Some processing here, for CAM, this would come from app
  # routine_dat0 <- read_csv(
  #   paste0(routinedata_dir, "/dat_combi_",
  #          indicator_select,  ".csv")) |> 
  #   mutate(indicator = indicator_select)
  # # routine_dat has indicator_name (name in routine) and 
  # # indicator (indicator name from survey data
  # routine_dat  <-
  #   routine_dat0  |>
  #   filter(worst_notmissing >= 90,
  #          worst_notoutliers >= 90,
  #          worst_abs_diff_level < 0.2,
  #          worst_rr >= 60) |>
  #   #|>
  #   #  filter(!is.na(diff_roc))
  #   # remove countries w/o any nonNA diff_roc
  #   group_by(iso) |>
  #   filter(sum(!is.na(diff_roc)) > 0) |>
  #   ungroup() |>
  #   mutate(sd_routine_roc = 0,
  #          sd_routine = 0) |>
  #   mutate(worst_combi =
  #            worst_rr/100*worst_notmissing/100*worst_notoutliers)

  # routine_dat_use <- 
  #   routine_dat |> 
  #   filter(iso %in% iso_select)

  # or if we want to use dummy data
  routine_dat_use <- readr::read_csv(here::here("data_raw/routine_toydata.csv")) |>
  # add iso
  dplyr::mutate(iso = iso_select,
  # add indicator name (as per routine data naming)
            indicator_name = dplyr::case_when(
              indicator_select == "anc1trimester" ~ "anc",
              indicator_select == "vmsl" ~ "measles2",
              indicator_select == "ideliv" ~ "instdeliveries",
              indicator_select == "vdpt" ~ "penta3",
              indicator_select == "anc4" ~ "anc4"
            ),
  # add indicator (from survey data naming)
            indicator = indicator_select)

}
routine_dat_use
```


```{r}
fit <- bayescoveragedeploy::fit_local_model(
          survey_df = dat |> dplyr::filter(iso %in% iso_select),
          indicator = indicator_select, 
          iso_select  = iso_select,
          routine_df = routine_dat_use
        )
```

Overview plot

```{r}
countryplot <- bayescoveragemodel::plot_estimates_local_all(
  results = fit,
  save_plots = FALSE)[[1]]
countryplot
```

Estimates

```{r}
fit$posteriors$temporal |>
  dplyr::select(iso, year, `50%`, `2.5%`, `97.5%`) 
```
