---
title: "Bayescoverage APP - overview"
author: "Leontine Alkema, May 11 2026"
format: pdf
editor: visual
---

Installation info is given in the readme.

Just loading all packages here to avoid issues (we may be able to remove some, eg brms).

```{r}
#| label: setup
library(bayescoveragemodel)
library(localhierarchy) # for check_nas...
library(tidyverse)
library(ggplot2)
#library(ggnewscale)
#library(ggpubr)
library(haven)
#library(stringr)
#library(readxl)
library(brms) # brms required for routine stuff
options(cmdstanr_warn_inits = FALSE)
```

Where data are stored:

```{r}
data_folder <- "data_raw" # for survey data 
routinedata_dir <- here::here("private/routinedata/")
# see note on wroking with routine dummy data below
```


Choose an indicator. Naming comes from survey data, options include

-   c("anc1trimester", "vmsl", "ideliv", "vdpt", "anc4") , with routine as available

-    c("bfexcl0_5", "ancq8" , "cci" , "sba" ), no routine data

```{r}
indicator_select <-"anc4" #"cci"#"vdpt"#"anc4"
```

Read in survey data and process

```{r}
dat0 <- read_dta(here::here(data_folder, "ICEH_all.long.dta")) %>%
  rename(r = r_raw, se = se_raw) 
# process for indicator_select
dat <- process_data(
  dat = dat0,
  regions_dat = bayescoveragemodel::regions_all,
  indicator = indicator_select)
```

Fitting for one country, use ISO to select

```{r}
# countries with survey data
# unique(dat$iso)
iso_select <- "RWA"
dat_use <- 
  dat %>% 
  filter(iso %in% iso_select)
```

Do we want to add routine data?

```{r}
add_routine <- ifelse(
  indicator_select %in% c("anc1trimester", "vmsl", "ideliv", "vdpt", "anc4"),
  TRUE, 
  FALSE)
add_routine
```

If yes, read in routine data. 

```{r}
if (!add_routine){
  routine_dat  <- routine_dat_use <- NULL
} else {
  # if we want to use real data
  # Some processing, we'll move this processing into a function.
  # routine_dat0 <- read_csv(
  #   paste0(routinedata_dir, "/dat_combi_",
  #          indicator_select,  ".csv")) %>% 
  #   mutate(indicator = indicator_select)
  # # routine_dat has indicator_name (name in routine) and 
  # # indicator (indicator name from survey data
  # routine_dat  <-
  #   routine_dat0  %>%
  #   filter(worst_notmissing >= 90,
  #          worst_notoutliers >= 90,
  #          worst_abs_diff_level < 0.2,
  #          worst_rr >= 60) %>%
  #   #%>%
  #   #  filter(!is.na(diff_roc))
  #   # remove countries w/o any nonNA diff_roc
  #   group_by(iso) %>%
  #   filter(sum(!is.na(diff_roc)) > 0) %>%
  #   ungroup() %>%
  #   mutate(sd_routine_roc = 0,
  #          sd_routine = 0) %>%
  #   mutate(worst_combi =
  #            worst_rr/100*worst_notmissing/100*worst_notoutliers)

  # routine_dat_use <- 
  #   routine_dat %>% 
  #   filter(iso %in% iso_select)

  # or if we want to use dummy data
  routine_dat_use <- read_csv(here::here("data_raw/routine_toydata.csv")) %>%
  # add iso
  mutate(iso = iso_select,
  # add indicator name (as per routine data naming)
            indicator_name = case_when(
              indicator_select == "anc1trimester" ~ "anc",
              indicator_select == "vmsl" ~ "measles2",
              indicator_select == "ideliv" ~ "instdeliveries",
              indicator_select == "vdpt" ~ "penta3",
              indicator_select == "anc4" ~ "anc4"
            ))

}
```



```{r}
fit <- fit_model(runstep = "local_national",
                       y = "invprobit_indicator",
                       se = "se_invprobit_indicator",
                       survey_df = dat_use,
                       routine_data = routine_dat_use,
                       #stan_file_path = stan_file_path_update,
                       chains = 4,
                       iter_sampling = 300,
                       iter_warmup = 150,
                       # validation_cutoff_year = 2010,
                       get_posteriors = TRUE)
```

Overview plot
```{r}
countryplot <- plot_estimates_local_all(
  results = fit,
  save_plots = FALSE)[[1]]
countryplot
```

Estimates 

```{r}
fit$posteriors$temporal %>%
  select(iso, year, `50%`, `2.5%`, `97.5%`) 
```

